PANCHANGE_data_preprocessing

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
Copied the PHQ block and adapted to OCI-R. Awaiting the actual data and variable names to complete the script. Need to add code to all sum scores to exclude participants with missing data.

Calculate sum score for GAD-7
Max should be 21.
```{r gad sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
gad.items_key_prepan <- c(1,1,1,1,1,1,1)

@@

Calculate sum score for PHQ-9
```{r phq sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
phq.items_key_prepan <- c(1,1,1,1,1,1,1,1,1)

@@

## COPING GLAD: GAD-7

>>>>

Calculate sum score for GAD-7
Max should be 21.

*** MD - need to adapt for participants with missing data (should be NA)
```{r gad sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
gad.items_key_prepan <- c(1,1,1,1,1,1,1)

@@

Calculate sum score for PHQ-9

*** MD - need to adapt for participants with missing data (should be NA)
```{r phq sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
phq.items_key_prepan <- c(1,1,1,1,1,1,1,1,1)

@@

# glad ocir

```{r glad ocir cols}
glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/glad/ocir_glad.rds")) #File doesn't exist yet
dim(glad.ocir.raw)
colnames(glad.ocir.raw)
```

```{r glad ocir cleaning}
glad.ocir.raw.id <- glad.ocir.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    ocir.variables_original_name = ocir.variables_new_name,
    ... ##Add variables to select and rename here
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(glad.ocir.raw.id)
# Inspect colnames
colnames(glad.ocir.raw.id)
#Differences
dim(glad.ocir.raw)[1]-dim(glad.ocir.raw.id)[1]
```

Calculate sum score for OCI-R

*** MD - need to adapt for participants with missing data (should be NA)
```{r ocir sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
ocir.items_key_prepan <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)

# Create vector with items that are included in sum score
ocir.items_prepan = c(
  "ocir.all_variables_listed_here",
  ##add variables to include in sum score
  )

# Calulate sum score
ocir.scored_items_prepan <- scoreItems(keys = ocir.items_key_prepan,
                                        items = glad.ocir.raw.id[ocir.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
glad.ocir.raw.id$ocir.sum_score_prepan <- ocir.scored_items_prepan$scores

# Look at values
glad.ocir.raw.id %>%
  descr(ocir.sum_score_prepan,
        stats = "common"
        )
```

```{r glad ocir head}
head(glad.ocir.raw.id)
```

```{r glad ocir summary}
summarytools::dfSummary(
  glad.ocir.raw.id,
  graph.col = F,
  valid.col = F
  )
```

# COPING GLAD: GAD-7
